MINOS Handover Plots

### 2023-07-05 minos/validation/handovers.Rmd
Sourced the validation/utils.r file in handovers.Rmd as should have already been done
Added some additional features to the html files that render from RNotebook scripts. Stuff like table of contents and some formatting

---
title: "MINOS Handover Plots"
output:
  html_document:
    df_print: paged
---

@@

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
```

@@

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

@@

@@

if (shall.we.save) {
  spaghetti_plot(spag, 'phealth',
               save = shall.we.save,
               save.path = save.path)
}

@@

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')

>>>>

---
title: "MINOS Handover Plots"
output:
  html_document:
    toc: true
    toc_float: true
      collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

@@

```{r, warning=FALSE}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

@@

rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
```

@@

spaghetti_plot(spag, 'phealth',
             save = shall.we.save,
             save.path = save.path)

@@

```{r, warning=FALSE}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')
